\section{Interface Requirements}

\begin{enumerate}
    \item \index{Display Method}\underline{\textsc{Display Method}} : Use of an \index{LED dot matrix display}LED dot matrix display.

    \item \underline{\textsc{Accuracy}} :The reading on the display must be accurate to ±1 minute.

    \item \underline{\textsc{Duration Of Activity}} : Must remain active only between 0700 to 1930 hours, powering on/off should be automated.

    \item \index{Display Mounting}\underline{\textsc{Display Mounting}} : Secure mounting to prevent theft. Mechanical fixation at unreachable height.

    \item \underline{\textsc{Accessibility for Visually Impaired}} :  Utilize PWM output or speech IC for accessibility.

    \item \index{Syncing Capacity}\underline{\textsc{Syncing Capacity}} : Not necessary for synchronization.

    \item \index{Budget Constraints}\underline{\textsc{Budget Constraints}} : To be Made as cost-efficient as possible.

    \item \index{Passenger Input}\underline{\textsc{Passenger Input}} : Prefer sensor-based input.

    \item \underline{\textsc{Audio Announcement}} : Consider installing an audio unit.

    \item \index{BUk Functionality}\underline{\textsc{BUk Functionality}} : No display on BUk, includes some visual confirmation LEDs.

    \item \underline{\textsc{Passenger Waiting Notification}} : Separate indicator integrated into BUk.

    \item \index{Error Indicator}\underline{\textsc{Error Indicator}} : The Display would read ‘999’ to indicate emergency or unforeseen delays

    \item \underline{\textsc{Feedback System}} : Are there any means for taking feedback from the users or for reporting issues related to bus services?

    \item \underline{\textsc{Resilient}} : Display is exposed to all Delhi weather conditions.
   
\end{enumerate}