\renewcommand{\glsnamefont}[1]{\makefirstuc{#1}}

\newglossaryentry{6/6 vision}{
    name={6/6 vision},
    description={denotes normal eyesight, where an individual can see details from a distance of 6 meters equivalent to what a person with typical vision sees at the same distance}
}
\newglossaryentry{24-hour clock}{
    name=24-hour clock,
    description={It is a timekeeping system where the hours beyond 12:00 are expressed without the use of AM or PM indicators.}
}
\newglossaryentry{accelerometer}{
    name=accelerometer,
    description={An instrument for measuring the acceleration of a body, which in practical terms means changes in speed or direction of a motion.}
}
\newglossaryentry{audio unit}{
    name={audio unit},
    description={Provides audio announcements using speakers regarding the estimated arrival time of the bus at specific bus stops.}
}
\newglossaryentry{DC/DC converter}{
    name=DC/DC converter,
    description={A DC-DC converter is an electronic circuit or electromechanical device that converts a source of direct current from one voltage level to another.}
}
\newglossaryentry{embedded system}{
    name=Embedded system,
    description={An embedded system is a specialized computer system designed to perform specific tasks within a larger system or device.}
}
\newglossaryentry{GPS}{
    name=GPS,
    description={GPS stands for Global Positioning System. It is a satellite-based navigation system that enables users to determine their precise location anywhere on Earth.}
}
\newglossaryentry{LED dot matrix display}{
    name=LED dot matrix display,
    description={A grid of light-emitting diodes (LEDs) arranged in rows and columns, allowing each LED to be individually controlled to display characters by selectively turning on or off specific LEDs in the matrix.}
}
\newglossaryentry{MPPT converter}{
    name=MPPT converter,
    description={Stands for  Maximum Power Point Tracking , it is a type of DC/DC converter commonly used in photovoltaic systems to optimize the power output of solar panels by continuously adjusting the operating point to maximize energy harvest from the panels.}
}
\newglossaryentry{PWM converter}{
    name=PWM converter,
    description={A type of power electronics device used to regulate the output voltage or current by controlling the duty cycle of a pulse-width modulated signal.}
}
\newglossaryentry{round trip}{
    name=round trip,
    description={Refers to a journey where a bus travels from a starting point to a destination and then returns back to the original starting point.}
}
\newglossaryentry{smog}{
    name=smog,
    description={A type of air pollution that consists of a mixture of smoke and fog, often caused by industrial emissions, vehicle exhaust, and atmospheric conditions.}
}
\newglossaryentry{sliding text animation}{
    name=sliding text animation,
    description={It is a visual effect over a display where text moves smoothly across the screen horizontally, vertically, or diagonally.}
}
\newglossaryentry{stall period}{
    name=stall period,
    description={Refers to a duration of time during which the system pauses temporarily until the situation is resolved, allowing the system to resume its intended function.}
}
\newglossaryentry{USB}{
    name=USB,
    description={Stands for Universal Serial Bus. It is a standardized interface commonly used for connecting peripherals to computers and other electronic devices.}
}
\newglossaryentry{ultrasonic sensor}{
    name=ultrasonic sensor,
    description={A device that utilizes ultrasonic waves, typically operating in the frequency range of 20 kHz to 200 kHz, to detect the presence and distance objects by emitting ultrasonic pulses and measuring the time it takes for the pulses to reflect back from objects.}
}
\newglossaryentry{U-turn}{
    name=U-turn,
    description={When a vehicle turns 180 degrees to reverse its direction and proceed in the opposite direction.}
}
\newglossaryentry{Wi-Fi}{
    name=Wi-Fi,
    description={Wireless Fidelity, is a technology that allows electronic devices to connect to the internet or communicate with one another wirelessly using radio frequencies.}
}
